---
title: "Explore"
author: "me"
date: "April 11, 2017"
output: html_document
---

#####DEPRECATED CODE#########

```{r eval=FALSE}
#hypothesis testing
instreams = numeric()
inmorethan5s = numeric()
inboths = numeric()


for (i in 1:10000) {
  bs = sample(subset$tweetID, size = nrow(subset), replace = TRUE)
  instreams = append(instreams, sum(bs %in% tweet_streaming)/nrow(subset))
  morethan5s = append(inmorethan5s, sum(bs %in% morethan5tweets$tweetID)/nrow(subset))
  inboths = append(inboths, sum(bs%in% morethan5tweets$tweetID &bs%in%tweet_streaming)/nrow(subset))
}

sum(sum(subset$inmorethan5)/nrow(subset) > inmorethan5s)/length(inmorethan5s)
sum(sum(subset$inmorethan5andstream)/nrow(subset) >inboths)/length(inboths)

inbothsdf = data.frame(inboths)
ggplot(inbothsdf) + geom_histogram(aes(x = inboths), bins = 20)
``` 

```{r eval = FALSE}
ggplot(alldata)
```

```{r eval = FALSE}
morethan5 = byusersubset[byusersubset$count > 5,]
subset$inmorethan5 = subset$usernameID %in% morethan5$Group.1
subset$inmorethan5andstream = subset$inmorethan5&subset$instream
sum(subset$instream)/nrow(subset) #41% of the firehose subset was represented in the stream
sum(subset$inmorethan5)/ nrow(subset) #69% of the tweets came from the more than 5 tweeters
nrow(morethan5)/nrow(subset) #2% of users have more than 5 tweets in the subset
sum(subset$inmorethan5andstream)/nrow(subset) #31% of tweets were both in the stream and came from more than 5ers

morethan5tweets = subset[subset$usernameID %in% morethan5$Group.1,]
```
#######################
#######################
######################


```{r setup, include=TRUE}
require(twitteR)
require(ggplot2)
```

```{r}
path_time= "deborah_fields.txt"
path_streaming = "data/all_streaming_api.txt"
path_firehose = "data/all_firehose.txt"

alldata = read.table(path_time, sep = ",", colClasses = c("character"))
tweet_streaming = unlist(read.table(path_streaming, sep = "\n", colClasses = c("character")))
tweet_firehose = unlist(read.table(path_firehose, sep = "\n", colClasses = c("character")))
names(alldata) = c("time", "tweetID", "usernameID")

s = data.frame(tweet_streaming)
f = data.frame(tweet_firehose)

# stimes = merge(s, tweet_time) gg
# ftimes = merge(f, tweet_streaming) gg

(sum(s$tweet_streaming %in% alldata$tweetID)/nrow(s))
(sum(f$tweet_firehose %in% alldata$tweetID)/nrow(f))

which(!s$tweet_streaming %in% alldata$tweetID)
alldata$instream = (alldata$tweetID %in% tweet_streaming)
alldata$infirehose = (alldata$tweetID %in% tweet_firehose)

length(unique(alldata$usernameID))/nrow(alldata)


```
#########
Don't run the below block more than once a session, as it samples.
#########
```{r}
# byuser = aggregate(alldata$tweetID, by = list(alldata$usernameID), FUN = count)
# the above line was left to run overnight and still didn't complete. sad.

subset = alldata[sample(1:nrow(alldata), 500000),]
```

```{r}
byusersubset = aggregate(subset$tweetID, by = list(subset$usernameID), FUN = length)
names(byusersubset) = c('User ID', 'count')
subset$date = as.Date(subset$time)

```
##################
#################



Below, we generate an overall distribution. I manually select low, medium, and high volume users.
```{r}
bins = c(1,5, 25)

overall_ID_ranges= lapply(bins, 
                        function(i){
                          if(i == 1){
                            return(byusersubset[byusersubset$count<5,])
                          }
                          else if (i == 25){
                            return(byusersubset[byusersubset$count >= 25,])
                          } else {
                          byusersubset[byusersubset$count >= 5 & byusersubset$count<25,]
                          }
                          })
names(overall_ID_ranges) = c("LOW", 'MED', 'HIGH')
```

Below, I calculate counts of people that ever show up in the streaming API feed.
```{r eval = TRUE}
overallstats = numeric()
fromstreamstats = numeric()
alldata_stream = unique(alldata[alldata$instream,]$usernameID)
# for (i in 1:3){
#   rangedf = overall_ID_ranges[[i]]
#   instream = sum(rangedf$`User ID` %in% alldata_stream)/nrow(rangedf)
#   overallstats = append(overallstats, instream)
# }
for (i in 1:3){
  rangedf = overall_ID_ranges[[i]]
  inrange = sum(alldata_stream %in% rangedf$`User ID`)#/length(alldata_stream)
  fromstreamstats = append(fromstreamstats, inrange)
}
```

Now let's do some SRS. The sample size is 528592 elements, and the population size is 1280166. We sample without replacement. 
```{r}
totalsimstats = data.frame(LOW = 0, MED = 0, HIGH = 0)
for (k in 1:10000){
  simindices = sample(1:length(tweet_firehose), size = length(tweet_streaming))
  simulatedstream = unique(alldata[simindices,]$usernameID)
  simstreamstats = numeric()
  for(i in 1:3){
    
    rangedf = overall_ID_ranges[[i]]
    inrange = sum(simulatedstream %in% rangedf$`User ID`)#/length(simulatedstream)
    simstreamstats = append(simstreamstats, inrange)
  }
  totalsimstats[k,] = simstreamstats
}
```

Calculating a p value
```{r}
chisquare = function(O,E){
  sum((O-E)**2/E)
}
totalsimstatschisquare = numeric()
firehosecounts = c(44118, 6089, 2377)
for (i in 1:nrow(totalsimstats)){
  totalsimstatschisquare = append(totalsimstatschisquare, 
                                  chisquare(totalsimstats[i,], firehosecounts *528592/1280166))
}
samplechisquare = chisquare(fromstreamstats, firehosecounts)

print(samplechisquare)

sum(samplechisquare < totalsimstatschisquare)/length(totalsimstatschisquare)

as.data.frame(totalsimstatschisquare)
ggplot(as.data.frame(totalsimstatschisquare), aes(x = totalsimstatschisquare)) + geom_histogram()
```


Generate a list of appearance frequencies of userIDs
```{r}
appearances = numeric()
userappearance = character()
for (i in unique(alldata$usernameID)){
  appearances = append(appearances, sum(alldata$usernameID == i))
  userappearance = append(userappearance, i)
}
```

```{r}
appearancesdf$num = 1:nrow(appearancesdf)
appearancesdf$appearances = sort(appearancesdf$appearances)
appearancesdf$appfact = cut(appearancesdf$appearances, c(0, 5, 25, 1000))
levels(appearancesdf$appfact) = c(levels(appearancesdf$appfact),(as.character(">1000")))
appearancesdf$appfact[is.na(appearancesdf$appfact)] = as.factor(as.character(">1000"))
# ggplot(appearancesdf, aes(x = appfact)) + geom_bar() + 

summarybrackets = ddply(appearancesdf, .(appfact), summarize, y=length(appfact))
tweetsperbracket = ddply(appearancesdf, .(appfact), summarize, y = sum(appearances))
ggsave("users.jpg", ggplot(summarybrackets, aes(x = appfact, y = y, fill = appfact)) + geom_bar(stat = "identity") + labs(x = "Number of appearances per User", y = "Number of users in bracket", title = "Number of users per tweet bracket") + guides(fill=guide_legend(title="Bracket")))

ggsave("tweets.jpg", ggplot(tweetsperbracket, aes(x = appfact, y = y, fill = appfact)) + geom_bar(stat = "identity")+ labs(x = "Number of appearances per User", y = "Total tweets of users in bracket", title = "Number of tweets per tweet bracket") + guides(fill=guide_legend(title="Bracket")))






```


Let's look at per days.

```{r}
alldata$day = as.Date(alldata$time)

alldata$day = as.factor(alldata$day)

byday = function(day){
  alldata[alldata$day == day, ]
}

daylist = lapply(levels(alldata$day), byday)

aggbyID = function(df){
  aggregate(df$tweetID, by = list(df$usernameID), FUN = length)
}

daylistusersubset = lapply(daylist, aggbyID)


 
usersubsetting = function(df){
  lapply(bins, function(i){
                        if(i == 1){
                          return(df[df$x<5,])
                        }
                        else if (i == 25){
                          return(df[df$x >= 25,])
                        } else {
                        df[df$x >= 5 & df$x<25,]
                        }
                        })
}

daylistusersubsetbybracket = lapply(daylistusersubset, usersubsetting)

```

```{r}
bracketstatsbyday = function(lst, thisday){
  fromstreamstatsbyday = numeric()
  alldata_stream_day = unique(alldata[alldata$day == thisday,][alldata$instream,]$usernameID)
  for (i in 1:3){
    rangedf = lst[[i]]
    inrange = sum(alldata_stream_day %in% rangedf$`Group.1`)/length(alldata_stream_day)
    fromstreamstatsbyday = append(fromstreamstatsbyday, inrange)
    print(length((alldata_stream_day)))
  }
  return(fromstreamstatsbyday)
  
  
}


sumstatsbyday = list()
for (i in 1){
  
  sumstatsthisday = bracketstatsbyday(daylistusersubsetbybracket[[i]], levels(alldata$day)[i])
  sumstatsbyday = append(sumstatsbyday, sumstatsthisday)
}




```

```{r}
ggsave("userhist.jpg",ggplot(byusersubset, aes(x= count)) + geom_histogram(bins = 100) + scale_x_log10())
```



